Appendix to \"Fast approximate Bayesian inference for small-area estimation

### 2023-05-09 src/docs_paper/appendix-word.Rmd
Add word version of appendix for Rachel

---
title: Appendix to "Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model"
author:
  - Adam Howes^[Department of Mathematics, Imperial College London]
  - Alex Stringer^[Department of Statistics and Actuarial Science, University of Waterloo]
  - Seth R. Flaxman^[Department of Computer Science, Oxford University]
  - Jeffrey W. Eaton^[Department of Infectious Disease Epidemiology, Imperial College London]
output:
  pdf_document:
    toc: yes
    number_sections: yes
    keep_tex: yes
    includes:
      in_header: preamble.tex
bibliography: citations.bib
cls: imsart.cls
---

@@

# Inferential algorithm

```{r algorithm-flowchart, fig.cap="Flowchart describing the algorithm we propose (work in progress)."}
knitr::include_graphics("depends/algorithm-flowchart.pdf")
```

@@

```{r simplified-naomi, fig.cap="Directed acyclic graph describing the simplified Naomi model (work in progress)."}
knitr::include_graphics("depends/simplified-naomi.pdf")
```

# \textsc{C++} `TMB` user template

@@

This section contains C++ `TMB` code for the negative log-posterior of the simplified Naomi model
For ease of understanding, Table \ref{tab:tmb-lookup} provides correspondence between the mathematical notation used in Section \ref{sec:math} and the variable names used in the `TMB` code, for all hyperparameters and latent field parameters.
For further reference on the `TMB` software see `https://kaskr.github.io/adcomp/_book`, or on the method see @kristensen2016tmb.

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines("naomi_simple.cpp")}
```

# MCMC convergence and suitability

We assessed MCMC convergence and suitability using a range of graphical and numerical tests. These included the potential scale reduction factor $\hat R$, bulk and tail effective sample size (ESS), autocorrelation decay plots, univariate traceplots, pairs density plots, and NUTS specific divergent transition and energy assessments.

For the time being, this analysis is available from `athowes.github.io/elgm-inf/mcmc-convergence`.
Once the MCMC results are finalised, the analysis will be moved to this appendix and expanded upon.
The following draft text and references may be useful in that expanded write-up.

- Improved $\hat R$ statistic from @vehtari2021rank. Recommended only to use the sample if the value is less than 1.05.
- ESS and autocorrelation related to efficiency
- Traceplots helpful for diagnosis of problems
- Pairs density plots helpful for understanding relationships between parameters, including possible identifiability issues
- Energy plot from @betancourt2017conceptual

>>>>

---
title: "Appendix to \"Fast approximate Bayesian inference for small-area estimation
  of HIV indicators using the Naomi model\""
author:
- Adam Howes^[Department of Mathematics, Imperial College London]
- Alex Stringer^[Department of Statistics and Actuarial Science, University of Waterloo]
- Seth R. Flaxman^[Department of Computer Science, Oxford University]
- Jeffrey W. Eaton^[Department of Infectious Disease Epidemiology, Imperial College
  London]
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
    number_sections: yes
    keep_tex: yes
    includes:
      in_header: preamble.tex
bibliography: citations.bib
cls: imsart.cls
---

@@

@@

@@
